Universal Anonymous Signatures

### 2022-08-13 prism-backend/research/gsac/app-related-proofs.tex
Added proof sketch for hide-iss.

\begin{proof}
  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and
  answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
  produced a credential for ring $\pk_i \in R$, \advB makes a call to its
  \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv does.
  \qed
\end{proof}

@@

  Note that, if $\adv$ wins its game, it means that the public keys of the
  issuers in $R$ all belong to uncorrupted users. Since the signature is
  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
  it is also accepted by \Verify in the \UAS non-frameability game. But,
  moreover, given the construction of $Verify$ in \CUASRing, there is some
  honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
  in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
  oracle, then by construction there cannot exist a matching entry in the
  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
  this probability must be negligible.
  %
  \qed
\end{proof}

>>>>

\begin{proof}
  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and
  answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv does.
  \qed
\end{proof}

@@

  Note that, if $\adv$ wins its game, it means that the public keys of the
  issuers in $R$ all belong to uncorrupted users. Since the signature is
  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
  it is also accepted by \Verify in the \UAS non-frameability game. But,
  moreover, given the construction of $Verify$ in \CUASRing, there is some
  honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
  in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
  oracle, then by construction there cannot exist a matching entry in \advB's
  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
  this probability must be negligible.
  %
  \qed
\end{proof}

### 2022-08-13 prism-backend/research/gsac/app-uas-proofs.tex
Added proof sketch for hide-iss.

  \paragraph{(b) All used credentials were correctly issued.} %
  Since issuers are assumed to be honest, we have access to the $\trans[\cid_i]$
  transcript for all credentials involved in producing the signature. Given
  simulation extractability of $\NIZK^{\Issue}$, \ExtractIssue outputs a valid
  witness $(\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
  \rbrace_{j\in[n_j]})$ from each $\trans[\cid_i]$. This, concretely, implies
  that the $\yissue^i$ value available in $\trans[\cid_i]$ matches the one
  output by \fissue. Similarly, due to simulation extractability, the set of
  credentials $\lbrace \cid_{i,j}\rbrace_{j\in[n_i]}$ used to request credential
  $\cid_i$ cannot include credentials owned by different users, as this
  condition is ensured by $\NIZKRel_{\Issue}$. Thus, $\uid = \OWNR[\lbrace
  \cid_{i,j} \rbrace_{j\in[n_i]}] \neq \bot$. Now, assume that $\uid \notin \HU
  \cup \CU$. This, in addition to the fact that {\usk}s are produced uniformly
  at random, means that $\cred_i$ is not bound to a \usk owned by a known
  user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
  which only accept request from known {\uid}s (either in \HU or \CU,
  respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
  produced via an honest query, which breaks the one-more forgery property of
  \SBCM.

@@

>>>>

  \paragraph{(b) All used credentials were correctly issued.} %
  Since issuers are assumed to be honest, we have access to the $\trans[\cid_i]$
  transcript for all credentials involved in producing the signature. Given
  simulation extractability of $\NIZK^{\Issue}$, \ExtractIssue outputs a valid
  witness $(\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
  \rbrace_{j\in[n_j]})$ from each $\trans[\cid_i]$. This, concretely, implies
  that the $\yissue^i$ value available in $\trans[\cid_i]$ matches the one
  output by \fissue. Similarly, due to simulation extractability, the set of
  credentials $\lbrace \cid_{i,j}\rbrace_{j\in[n_i]}$ used to request credential
  $\cid_i$ cannot include credentials owned by different users, as this
  condition is ensured by $\NIZKRel_{\Issue}$. Thus, $\uid = \OWNR[\lbrace
  \cid_{i,j} \rbrace_{j\in[n_i]}] \neq \bot$. Now, assume that $\uid \notin \HU
  \cup \CU$. This, in addition to the fact that {\usk}s are produced uniformly
  at random, means that $\cred_i$ is not bound to a \usk owned by a known
  user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
  which only accept requests from known {\uid}s (either in \HU or \CU,
  respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
  produced via an honest query, which breaks the one-more forgery property of
  \SBCM.

@@

\subsection{Security of $\CUASGen^{hide-iss}$}
\label{sapp:sec-hide-iss}

The only aspect that changes from \CUASGen to $\CUASGen^{hide-iss}$ is the
relationship used for signing, where we hide the specific issuer who produced
the (now only) credential used for signing.
%
This change does not affect the proofs for issuance anonymity, nor signature
anonymity.
%
Concerning unforgeability, note that the credential that is used to produce the
\UAS signature still needs to originate from a \uid in either \HU or \CU.
Otherwise, such credential, extracted by \ExtractSign, is a forgery and breaks
the one-more forgery property of \SBCM. Moreover, such credential must exist,
due to simulation extractability of the underlying NIZK.
%
The proof for non-frameability is also unaffected by the change.

Thus, if \CUASGen is a secure \UAS scheme, so is $\CUASGen^{hide-iss}$.

### 2022-08-13 prism-backend/research/gsac/formal-uas.tex
Updated proofs for UAS=>MPS.
Added proof sketch for hide-iss.

\begin{figure}[htp!]  
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\scid] \in \HU \land
      (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.
    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\WREG,\OBTAIN,\SIGN$.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

We show the modified NIZK relation for signing in \figref{fig:nizk-ring}. For
notational simplicity, we restrict to just one credential per signature.
%
Modelling-wise, no changes are needed. Perhaps notably, in this case, the
anonymity property is still required to enforce that both challenge signatures
are associated to the same set of (potential) issuers -- otherwise, it is
trivial to distinguish signatures.

@@

\paragraph{Interactive Credential Presentation.}
\todo{Does this meet the model? If not, we should move this elsewhere.}
In \appref{app:interactive-uas}
we show how to convert the non-interactive signing and verification processes
into an interactive protocol. While the transformation is quite straightforward,
it is of high relevance for real world use cases.

>>>>

\begin{figure}[htp!]  
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \in \HU: % \land
      %(\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.
    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\WREG,\OBTAIN,\SIGN$.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

We show the modified NIZK relation for signing in \figref{fig:nizk-ring}. For
notational simplicity, we restrict to just one credential per signature.
%
Modelling-wise, no changes are needed. Perhaps notably, even in this case, the
anonymity property is still required to enforce that both challenge signatures
are associated to the same set of (potential) issuers -- otherwise, it is
trivial to distinguish signatures. Security for $\CUASGen^{hide-iss}$, based on
security of \CUASGen, is sketched in \appref{sapp:sec-hide-iss}.

@@

\paragraph{Interactive Credential Presentations.}
\todo{Does this meet the model? If not, we should move this elsewhere.}
In \appref{app:interactive-uas}
we show how to convert the non-interactive signing and verification processes
into an interactive protocol. While the transformation is quite straightforward,
it is of high relevance for real world use cases.
